### 2016-11-18 build/paper.tex
pdf/tex build

\hypertarget{refs}{}
\hypertarget{ref-Katz2013}{}
{[}1{]} Y. Katz, ``Extend the web forward,'' 2013.

\hypertarget{ref-Walton2016}{}
{[}2{]} P. Walton, ``Houdini: Maybe the most exciting development in css
you've never heard of,'' 2016.

\hypertarget{ref-Berner2016}{}
{[}3{]} D. Berner, ``Not an imposter: Fighting front-end fatigue,''
2016.

\hypertarget{ref-Baldwin2006}{}
{[}4{]} C. Y. Baldwin and K. B. Clark, ``Modularity in the design of
complex engineering systems,'' in \emph{Complex engineered systems:
Science meets technology}, D. Braha, A. A. Minai, and Y. Bar-Yam, Eds.
Berlin, Heidelberg: Springer Berlin Heidelberg, 2006, pp. 175--205.

\hypertarget{ref-Keith2014}{}
{[}5{]} J. Keith, ``Web components,'' 2014.

>>>>

\hypertarget{refs}{}
\hypertarget{ref-Katz2013}{}
{[}1{]} Y. Katz, ``Extend the web forward,'' 2013 {[}Online{]}.
Available:
\url{http://yehudakatz.com/2013/05/21/extend-the-web-forward/}

\hypertarget{ref-Walton2016}{}
{[}2{]} P. Walton, ``Houdini: Maybe the most exciting development in css
you've never heard of,'' 2016 {[}Online{]}. Available:
\url{https://www.smashingmagazine.com/2016/03/houdini-maybe-the-most-exciting-development-in-css-youve-never-heard-of}

\hypertarget{ref-Berner2016}{}
{[}3{]} D. Berner, ``Not an imposter: Fighting front-end fatigue,'' 2016
{[}Online{]}. Available:
\url{https://www.smashingmagazine.com/2016/11/not-an-imposter-fighting-front-end-fatigue/}

\hypertarget{ref-Baldwin2006}{}
{[}4{]} C. Y. Baldwin and K. B. Clark, ``Modularity in the design of
complex engineering systems,'' in \emph{Complex engineered systems:
Science meets technology}, D. Braha, A. A. Minai, and Y. Bar-Yam, Eds.
Berlin, Heidelberg: Springer Berlin Heidelberg, 2006, pp. 175--205
{[}Online{]}. Available: \url{http://dx.doi.org/10.1007/3-540-32834-3_9}

\hypertarget{ref-Keith2014}{}
{[}5{]} J. Keith, ``Web components,'' 2014 {[}Online{]}. Available:
\url{https://adactio.com/journal/7431}
